---
title: "p8105_hw5_zf2352"
author: "Zhenkun Fang"
date: "2024-11-11"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
knitr::opts_chunk$set(echo = TRUE)

set.seed(123)
```

# Problem 1

```{r}
duplicated_birthday = function(n) {
  
  birthdays = sample(1:365, n, replace = TRUE)
  
  return(length(birthdays) != length(unique(birthdays)))
}

duplicated_birthday(25)
```

```{r}
group_size = 2:50
probabilities = numeric(length(group_size))
simulations = 10000

for (i in seq_along(group_size)) {
  n = group_size[i]
  duplicates = replicate(simulations, duplicated_birthday(n))
  probabilities[i] = mean(duplicates)
}

results <- data.frame(GroupSize = group_size, Probability = probabilities)
print(results)
```

```{r}
plot(group_size, probabilities, type = "o", col = "blue",
     xlab = "Group Size", ylab = "Probability of Shared Birthday",
     main = "Probability of at Least Two People Sharing a Birthday")
```

The plot shows that as the group size increases from 2 to around 23, the probability of at least two people sharing a birthday increases rapidly. At a group size of approximately 23, the probability exceeds 0.5, meaning that there's a greater than 50% chance that at least two people will share a birthday. The plot shows a steady increase in probability up to around group size 40, after which the probability seems to plateau near 1.

# Problem 2

```{r}
n = 30
sigma = 5
alpha = 0.05

sim_mean_sd = function(n, mu, sigma) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  t_test_result = t.test(sim_data$x, mu = 0)
  tidy_result = tidy(t_test_result)
  
  sim_data |> 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x),
      p_value = tidy_result$p.value
    )
}
```

```{r}
output = vector("list", 5000)

for (i in 1:5000) {
  output[[i]] = sim_mean_sd(n, mu = 0, sigma)
}

sim_results_0 = bind_rows(output)
summary(sim_results_0)
```

```{r}
mu_values = 1:6
n_datasets = 5000
power_results = data.frame(mu = mu_values, power = numeric(length(mu_values)))


for (mu in mu_values) {
  p_values = replicate(n_datasets, sim_mean_sd(n, mu, sigma))
  power = mean(p_values < alpha)
  power_results[power_results$mu == mu, "power"] = power
}
```

```{r}
ggplot(power_results, aes(x = mu, y = power)) +
  geom_line(color = "blue") +
  geom_point(color = "red") +
  labs(title = "Power of the Test vs. Effect Size (Mu)",
       x = "True Value of Mu",
       y = "Power of the Test") +
  theme_minimal()
```

